Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-09-19 manuscript.Rmd
Fixed small multiples. One minor edit still needed.

ggplot(combined_reduced,  aes(Year, Documents, colour = DataBase)) +
     geom_line() + 
     facet_wrap(~ Journal)

@@

 sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
 sm.scopus.merged <- group_by(sm.scopus.merged, Journal) %>%
     mutate(Overall.Scopus = sum(Documents, na.rm=TRUE)) %>%
     ungroup()
# 
 # Create labels for the facets
 Overall.N <- distinct(sm.scopus.merged, Abbrev) 
 lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
 lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
 lab <- paste(lab1, lab2, sep="\n")
 xpos = rep(1999, 79)
 ypos = rep(180, 79)
 ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
     rename(Abbrev = Overall.N.Abbrev)

@@

 plotSmallMultiples.a <-  ggplot(new.data,  aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = reduced.smallmult.df[reduced.smallmult.df$Journal %in% titles.reduced.a, ], 
               aes(Year, Documents), colour = "#533c99", alpha = .80) + 
     facet_wrap(~ Abbrev) + 
    geom_text(data = reduced.ldata, aes(x =xpos, y = ypos, label = lab), size = 5) +
     theme_bw() +
     theme(strip.text.x = element_text(size = 12)) + 
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size = 10)) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
     annotate("segment", x = 1992, xend = 1995, y = 190, yend = 190, colour = "#e66101") + 
     annotate("segment", x = 1992, xend = 1995, y = 170, yend = 170, colour = "#533c99") 
     #ggtitle("Figure 1. Comparison of Historical Database with Scopus\n for Journals with Highest Output (1989 - 2013)") + 
     # theme(plot.title = element_text(size = 19))
     # 
#ggsave(file = "scopusComparison.png", plotSmallMultiples.a)

>>>>

combined_reduced$Journal <- factor(combined_reduced$Journal, levels = c("Families in Society", "Social Work", "British Journal of Social Work", "Journal of Gerontological Social Work", "Research on Social Work Practice", "Social Work in Health Care", "International Social Work", "Health & Social Work", "Journal of Social Work Education") )

# Create labels for the facets
journalOutput <- distinct(sm.scopus.merged, Journal)

ann_scopus <- select(journalOutput, Journal, Overall.N)
ann_scopus <- ann_scopus[1:9, ]
ann_scopus$label <- paste0("N=", pretty(ann_scopus$Overall.N))

ggplot(combined_reduced,  aes(Year, Documents, colour = DataBase)) +
     geom_line(size = 1, alpha = .80) + 
     facet_wrap(~ Journal) +
     theme(strip.text.x = element_text(size = 2.5)) +
  theme_bw() + 
  theme(legend.position = "bottom", legend.text = element_text(size = 12)) + 
     scale_colour_discrete(guide = guide_legend(title = "Database"), breaks = c("HD", "Scopus"), labels = c("Historical Database", "Scopus")) + 
  scale_colour_manual(values = c(cp[2], cp[4]), labels = c("Historical Database", "Scopus"), guide = guide_legend(title = "")) + 
  ylab("Number of Articles") + 
  xlab("\nYear") +
     annotate("segment", x = 1992, xend = 1995, y = 190, yend = 190, colour = cp[2], size = 1, alpha = .80) + 
     annotate("segment", x = 1992, xend = 1995, y = 170, yend = 170, colour = cp[4], size = 1, alpha = .80) +
   geom_text(data = ann_scopus, aes(x = 1999, y =  170, label = label), colour = "black", size = 4)

@@

 sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
 sm.scopus.merged <- group_by(sm.scopus.merged, Journal) %>%
     mutate(Overall.Scopus = sum(Documents, na.rm=TRUE)) %>%
     ungroup()
# 
 # Create labels for the facets
 Overall.N <- distinct(sm.scopus.merged, Abbrev) 
 lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
 lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
 lab <- paste(lab1, lab2, sep="\n")
 xpos = rep(1999, 79)
 ypos = rep(180, 79)
 ldata <- data.frame(xpos, ypos, lab, Overall.N$Journal)

@@

 plotSmallMultiples.a <-  ggplot(new.data,  aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = reduced.smallmult.df[reduced.smallmult.df$Journal %in% titles.reduced.a, ], 
               aes(Year, Documents), colour = "#533c99", alpha = .80) +

     facet_wrap(~ Abbrev) + 
    geom_text(data = reduced.ldata, aes(x =xpos, y = ypos, label = lab), size = 5) +
     theme_bw() +
     theme(strip.text.x = element_text(size = 12)) + 
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size = 10)) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
     annotate("segment", x = 1992, xend = 1995, y = 190, yend = 190, colour = "#e66101") + 
     annotate("segment", x = 1992, xend = 1995, y = 170, yend = 170, colour = "#533c99") 
     #ggtitle("Figure 1. Comparison of Historical Database with Scopus\n for Journals with Highest Output (1989 - 2013)") + 
     # theme(plot.title = element_text(size = 19))
     # 
#ggsave(file = "scopusComparison.png", plotSmallMultiples.a)
